Astrophysical calibration of gravitational-wave detectors

### 2015-09-28 docs/cosmic_cal.tex
Minor changes I forgot to commit last week.

% this is copied text for reference !! 
%Estimates for jet beaming are θj ∼ 5◦ for lGRBs and θj ∼ 5 − 15◦ for sGRBs
%(Burrows et al. 2006, Grupe et al. 2006, Fong et al. 2012). Beaming angles for
%sGRBs are still highly uncertain. The beaming factors fb = 1 − cos θj ≃ θj2/2
%are roughly 1/300 for lGRBs and 1/30 for sGRBs. Based on the observed rate of
%sGRBs by Swift, Coward et al. (2012) estimate a LVC detection rateof∼3−30yr−1
%forθj ≃ 15◦. Chen&Holz(2013)claim3−7yr−1 forGRBGW+EM detections. Kelley et al.
%(2013) estimate the rate of Swift or Fermi observations joint with LVC
%detections to be ∼0.07 yr−1. Siellez, Boe ̈r, & Gendre (2014) consider current
%and future high energy missions and estimate a rate of simultaneous GW+EM
%detections of ∼0.1 − 4 yr−1 in the LVC era. Wanderman & Piran (2015) estimate a
%co-detection rate LVC+Fermi of 0.1 − 1 yr−1 and LVC+Swift of 0.02 − 0.14 yr−1.

% discuss joint-event rates
\cm{Discuss the expected rate of joint detections}\\

>>>>

% discuss joint-event rates
The predicted detection rates of \ac{BNS} events (irrespective of an \ac{sGRB}
counterpart) are derived from three main sources, population sythesis models,
extrapolations based on known galactic \ac{BNS} systems, and from observations
of \ac{sGRB} events. Various studies using the first two methods have been
compiled into an overall detection rate of $0.2$--$200$ \ac{BNS} events per
year~\cite{2013arXiv1304.0670L}~\cite{2010CQGra..27q3001A}~\footnote{We should
briefly mention why the rates differ by a factor of 2.  I can't remember right
now.}. In~\cite{2012MNRAS.425.2668C} using the rate of observed \acp{sGRB} and
assuming a beaming angle of $15^{o}$ a similar event rate of $1$--$180$ is
obtained. The beaming angle is the primary factor in determining the fraction
of detected \ac{GW} \ac{BNS} signals with an \ac{EM} \ac{sGRB} counterpart and
is unfortunately highly uncertain.  Various authors have provided estimates on
the rate of joint detections to be in the range $0.02$--$7$ per
year~\cite{2013PhRvL.111r1101C},~\cite{Kelley:2012fl},~\cite{2014arXiv1405.2254S},~\cite{2015MNRAS.448.3026W}.
